Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-01-30 PAPER.tex
Folded back in Carina's text about no bootstrapping. Still need normalization explanation

We smooth the 2D distribution of $P_{in}$ vs. $P_{out}$ using kernel density estimators\citep{scott2008kernel}. The result, for inverse covariance weighting, is shown in the left plot of Figure \ref{fig:sigloss_transfercurve}.  Although we only show figures for one $k$ value, we note that 
the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately).Bayes' rule then simply instructs us to fix $\phat_{x}$ at our measured value, essentially reading Figure \ref{fig:sigloss_transfercurve} horizontally and reinterpreting Equation \eqref{eq:Bayes} as a function of $p(P_{in})$. The final result can then be normalized to give $p(P_{\rm eor} | \phat_{x})$. If $\phat_{x}$ itself does not take on a single value but is itself a distribution (for our analysis, this comes from bootstrapping), then one simply repeats the process for every single point on the distribution of $\phat_{x}$, to find the distribution of $P_{\rm eor}$. In Figure \ref{fig:sigloss_transfercurve}, the peak of our data distribution $
\widehat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines. From the left plot (inverse covariance weighting), one can eyeball that a data value of $10^{5} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a 
value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim1000$. Performing a summation and normalization for the entire distribution of $\widehat{\textbf{p}}_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens. We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals. \dcj{Normalization needs an equation}

>>>>

We smooth the 2D distribution of $P_{in}$ vs. $P_{out}$ using kernel density estimators\citep{scott2008kernel}. 
The result, for inverse covariance weighting, is shown in the left plot of Figure \ref{fig:sigloss_transfercurve}.  
Although we only show figures for one $k$ value, we note that 
the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately).Bayes' rule 
then simply instructs us compute $p(\phat_{x})$, multiply it horizontally across Figure 
\ref{fig:sigloss_transfercurve} horizontally as defined in Equation \eqref{eq:Bayes} to get $p(P_{in})$. The final 
result can then be normalized to give $p(P_{\rm eor} | \phat_{x})$. 
\dcj{Need to write down the normalization for \eqref{eq:Bayes}}
The width of the distribution of  $\phat_{x}$ itself is defined as a  gaussian with the mean $\phat_{x}$ and 
variance determined from the bootstrap process.

Inspection of the transfer function plot in Figure \ref{fig:sigloss_transfercurve} gives a sense of what the result should be.  The peak of our data distribution $
\widehat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines. From the left plot (inverse covariance weighting), one can eyeball that a data value of $10^{5} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a 
value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim1000$. Performing a summation and normalization for the entire distribution of $\widehat{\textbf{p}}_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens. We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals. \dcj{Normalization needs an equation}
